Multi-task learning in Computer Vision

### 2020-05-27 1-Introduction.tex
Add introduction texts

Multi-task learning proposes some solutions to these problems but makes the training process more difficult. Still, in some cases, it is something that has to be done to get a good enough inference time and accuracy on the problem at hand. Many modern computer vision models already feature an ImageNet backbone as a part of the classifier, so this is a good part of the network to consider for sharing, but finding which tasks and how much can be shared is a difficult problem to solve.

\section{Scope of study}
In this thesis, we will study state-of-the-art solutions to some computer vision problems, like image classification, object detection, and text recognition. Then we will train classifiers that solve these problems using various data sets and try to combine them to produce a single multi-task network using multi-task learning. We will then evaluate how easy and effective it is to share the weights within similar and different tasks.

>>>>

Multi-task learning proposes some solutions to these problems but makes the training process more difficult. Still, in some cases, it is something that has to be done to get a good enough inference time and accuracy on the problem at hand. Many modern computer vision models already feature an ImageNet backbone as a part of the classifier, so this is a good part of the network to consider for sharing. 
However, finding which tasks and how much can be shared is a difficult problem to solve.

\section{Scope of study}
In this thesis, we will present state-of-the-art solutions to fundamental computer vision problems, like image classification and object detection.
We will present the architectures of these models and show how the ImageNet backbones are an essential part of solving these problems.
Using the presented solutions, we will make use of various data sets to train multi-task models and evaluate the effects of training multi-task models.

\section{Structure of thesis}
Chapter 2 will present some basic terminology for describing convolutional neural networks that will be used throughout the thesis.
We won't cover the very basics of neural networks or the exact inner workings of convolutional neural networks, and refer to \citep{deep-learning} for studying those details.

Chapter 3 covers the modern image classification models, describing their architecture and how to train them.
We will also describe why the ImageNet is such a valuable data set to so many problems.
We will demonstrate the significance of the ImageNet models by defining transfer learning and describing how it is instrumental in solving small-scale problems with the ImageNet models as backbones.

Chapter 4 covers the basics of multi-task learning as it relates to computer vision.
We will define multi-task learning and see how it relates to transfer learning.
Also, the basic differences of multi-task training to a single-task setting are described, and some examples of multi-task models are shown.
Finally, the theoretical benefits and issues that may arise are talked about and demonstrated using some examples.

Chapter 5 describes what object detection is and how to evaluate object detection models.
We will also briefly discuss the basic parts of an object detector and the difference between single and two-stage object detectors.
Finally, we will cover the EfficientDet architecture in detail and explain how to train an object detector by using it.

In chapter 6, we will cover the results of our experiments on training multi-task models.
The first experiment is about training image classifiers on plant imagery.
The second experiment is about training multi-label classifiers.
The third experiment covers training object detectors with multiple datasets.
The fourth experiment combines an object detector, an image classifier, and an image segmentation model into a single classifier.
Finally, we will summarize our experiences in training multi-task models and explain what problems we encountered.
